Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-18 main.tex
Questions

Generalizing to allow for contours to change throughout the execution,
nested lockstep noninterference is the contoured lockstep
hyperproperty where:

@@

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, the pair of truncated traces $\overline{(C,
    M)}_m$ and $\overline{(C, M')}_m$ is also in the set if $m < n$.

@@

\leo{..and the observations of each trace coincide, right?}

@@

\bcp{Not quite enough: Policies and properties needs to know where are the
  call and return sites.  So what we should do is to talk instead about ``$X$
  policies'' (i.e., make ``policy'' a type operator) and replace the initial
  $\CONTOURS$ argument to both policies and properties by an element of
  $X$.}

>>>>

Generalizing to allow for contours to change throughout the execution,
nested lockstep noninterference is the contoured lockstep hyperproperty
where: \bcp{Which parts of this are common to {\em all} contoured lockstep
  hyperproperties (i.e., which should be part of the definition of contoured
  lockstep hyperproperties) and which are specific to (nested) NI?}

@@

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, \bcp{where $n$ is the length of the traces,} the
  pair of truncated traces $\overline{(C, 
    M)}_m$ and $\overline{(C, M')}_m$ is also in the set if $m < n$ \bcp{or
    $n = \infty$}.

@@

\leo{..and the observations of each trace coincide, right?}\bcp{Yes, I guess
  so.}

\bcp{It feels like something is missing here: This definition seems to be
  requiring that secret data never affect observations, but our tester is
  ensuring something more: that inaccessible locations are not {\em changed}
(at least without also changing their tag to make them accessible).  Where
is that condition being imposed?}

@@

\bcp{Policies and properties need to know where are the call and return
  sites, and for this they need to be initialized with some
  application-specific information.  So it seems what we should do is to
  talk instead about ``$X$ policies'' (i.e., make ``policy'' a type
  operator) and replace the initial $\CONTOURS$ argument to both policies
  and properties by an element of $X$.}
